---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)

credentials <- readRDS("tests/testthat/testing_credentials.Rds")
```
# Castor API R Package
The intent of this package is to provide convenient access to study data in Castor via R.

## Package Structure
Access to data in the API comes in three forms:

1. Access to individual items (getStudyDataPoint, getStudy, getRecord, etc.)
2. Access to pages of items in a list (getStudyDataPoints, getStudies, getRecords, etc.)
3. Processed into a data frame for straightforward analysis (getStudyData)

## Installation

```r
# install.packages("remotes")
remotes::install_github("castoredc/castoRedc")
```

## Testing

If you want to test the package, for example when developing, please fill in create_testing_credentials.R.  
You should supply an example for each of the study, report, etc. 
Please make sure that the record has a value in the field.
And that the report step is a child of the report.

## Usage

See [https://helpdesk.castoredc.com/article/124-application-programming-interface-api](https://helpdesk.castoredc.com/article/124-application-programming-interface-api) about generating your credentials.  

_Note: It is recommended that you read [https://cran.r-project.org/web/packages/httr/vignettes/secrets.html](https://cran.r-project.org/web/packages/httr/vignettes/secrets.html) about managing your credentials._  

```{r example}
library(castoRedc)

castor_api <- CastorData$new(key = credentials$client_id, 
                             secret = credentials$client_secret, 
                             base_url = "https://data.castoredc.com")
```


```{r message=FALSE}
studies <- castor_api$getStudies()
```
```{r echo=FALSE, results='asis'}
knitr::kable(studies)
```


```{r message=FALSE}
(example_study_id <- studies[["study_id"]][1])
```


```{r message=FALSE}
fields <- castor_api$getFields(example_study_id)
```
```{r echo=FALSE, results='asis'}
knitr::kable(head(subset(fields, select = -field_summary_template), 3))
```


```{r message=FALSE}
steps <- castor_api$getSteps(example_study_id)
```
```{r echo=FALSE, results='asis'}
knitr::kable(steps)
```


```{r message=FALSE}
phases <- castor_api$getPhases(example_study_id)
```
```{r echo=FALSE, results='asis'}
knitr::kable(phases)
```

